Optimal coordination - general experiment analysis.

### 2019-06-19 voltagebudget/analysis/optimal_analysis.Rmd
Update imports
Update test vis for coincidence alg

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)
library(scales)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

@@

results <- NULL
for (n in 1:4){
  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], ".csv", sep=""))
  df$alg <- rep(alg_names[n], nrow(df))

@@

# Spikes
# Load ref spikes
ref <- read_csv("../data/stim1.csv")
ref$set <- rep("reference", nrow(ref))

# Load exp spikes
exps <- c(86, 87, 88, 89)
spikes <- NULL
for (n in 1:4){
  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], "_c0.2.csv", sep=""))
  df$set <- rep("experiment", nrow(df))

@@

```{r, fig.width=1.4, fig.height=0.8}
results %>% 
  filter(alg != "coincidence") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, linetype=alg)) +
  geom_line(size=0.6, alpha=0.9) +
  scale_linetype_manual(values=c("longdash", "solid", "dotdash"), name="Algorithm") +
  theme_classic() +
  labs(x="Error (ms)", y="Variance (ms)")
```

```{r, fig.width=1.0, fig.height=1.5}
spikes %>% 
  filter(alg != "coincidence") %>%
  ggplot(aes(x=ts, y=ns, color=set)) +
  geom_point(size=0.1) +
  facet_grid(alg~.) +
  scale_color_manual(values=c("black", "grey")) +
  theme_classic() +
  theme(
    legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

>>>>

```{r, message=FALSE}
library(ggplot2)
library(magrittr)
library(readr)
library(gridExtra)
library(readr)
library(scales)
library(dplyr)
library(NNTbiomarker)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
find_point <- function(x, y, point){
  i <- argmin(x, target = point)
  return(c(x[i], y[i]))
}

```

@@

results <- NULL
for (n in 1:4){
  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], ".csv", sep=""))
  df$alg <- rep(alg_names[n], nrow(df))

@@

# Spikes
# Load ref spikes
ref <- read_csv("../../data/stim1.csv")
ref$set <- rep("reference", nrow(ref))

# Load exp spikes
# exps <- c(86, 87, 88, 89)
exps <- c(110, 111, 112, 113)
spikes <- NULL
for (n in 1:4){
  # df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_c0.2.csv", sep=""))
  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_target0.01_spikes.csv", sep=""))
  df$set <- rep("experiment", nrow(df))

@@

```{r, fig.width=1.4, fig.height=0.8}
results %>% 
  filter(alg != "left") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, linetype=alg)) +
  geom_line(size=0.6, alpha=0.9) +
  # scale_linetype_manual(values=c("longdash", "solid", "dotdash", "dot"), name="Algorithm") +
  theme_classic() +
  labs(x="Error (ms)", y="Variance (ms)")
```

```{r, fig.width=1.0, fig.height=1.5}
spikes %>% 
  filter(alg != "left") %>%
  ggplot(aes(x=ts, y=ns, color=set)) +
  geom_point(size=0.1) +
  facet_grid(alg~.) +
  scale_color_manual(values=c("black", "grey")) +
  theme_classic() +
  theme(
    legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.5, fig.height=1.5}
 spikes %>% 
  filter(alg != "left") %>% 
  filter(set == "experiment") %>%
  ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
  geom_point(size=2.3, alpha=1, shape=4) +
  geom_point(
    data=filter(filter(spikes, alg != "left"), set == "reference"),
    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=1, size=1.2) +
  facet_grid(alg~.) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0))
```
